---
title: "COVID-19 Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggmap)
library(tidyverse)
library(dplyr)
library(leaflet)
library(ggplot2)
library(viridis)
library(hrbrthemes)
library(plotly)
library(lemon)
library(lubridate)
library(zoo)
library(sqldf)
```

```{r include=FALSE}
Heat_Map_Data<- read.csv("Merged Data//Provincial_wc.csv")

options(scipen = 999)

``` 


```{r include=FALSE}
## Selecting Max values from Western Cape data  

infect_town<-Heat_Map_Data %>% group_by(Town) %>% slice(which.max(Infected)) %>%  arrange(Infected) %>% drop_na()

infect_town
```
```{r include=FALSE}

#Create Color gradient for Map of Western Cape
Col_Gradient<- c("green","red")
## create color pallet based on Gradient and Calibrated with global cases
pal<- colorFactor(Col_Gradient,infect_town$Infected)
infect_town<- infect_town %>% mutate(PopUp=paste(Town,"<br/>","Number of Infected People",Infected))
MapWC<- leaflet() %>% addTiles() %>% 
  addCircleMarkers(data = infect_town,lat = ~latitude,lng = ~longitude,color = ~pal(Infected),radius = ~3,popup = ~PopUp)

```


```{r include=FALSE}
# import global data
World_map_data<- read.csv("Merged Data/Global_Max_Country.csv")
```


```{r include=FALSE}


infect_World<- World_map_data

# Adding Pop-Up message to the data to be used in map 

infect_World<- infect_World %>% mutate(PopUp=paste(Country.Region,"<br/>","Number of Infected People:",Cases,
                                                   "<br/>","Number of deaths:",Deaths,"<br/>",
                                                   "Number of recoveries:",Recoveries
                                                   ))

```

```{r include=FALSE}
# Create color gradient for map 
Col_Gradient2<- c("green","red")
# create color pallet based on Gradient and Calibrated with global cases  
pal2<- colorFactor(Col_Gradient2,infect_World$Cases)
# Plotting Points on the map
Map_World<-leaflet() %>% addTiles() %>% 
  addCircleMarkers(data = infect_World ,lat = ~Lat,lng = ~Long,color = ~pal2(Cases),radius = ~3,popup = ~PopUp)

```

```{r include=FALSE}

# World map plot 
Map_WORLD_Merged<-leaflet()%>%
  addTiles() %>%
  addCircleMarkers(data = infect_World ,lat = ~Lat,lng = ~Long,color = ~pal2(Cases),radius = ~4,popup = ~PopUp)
  
```


# Global 


Column {data-width=650}
-----------------------------------------------------------------------

### World map

```{r}
Map_WORLD_Merged
```


Column {data-width=650}
-----------------------------------------------------------------------

### Top 20 Cases 

```{r}
# Arranging data from high to low based on cases 

topCases<- World_map_data %>% arrange(desc(Cases))
topCases$Country.Region<- factor(topCases$Country.Region , levels = topCases$Country.Region[order(topCases$Cases)])

# select and plot the first 20 
top20cases <- topCases[1:20,]%>% ggplot(aes(x=Country.Region, y=Cases)) +
  geom_bar(stat="identity", color="blue",fill="blue") + ggtitle("Top 20 most infected countries") + labs(y= "Total Confirmed Cases", x = "Country") + theme_bw() + theme(axis.text.x = element_text(angle = 45))

ggplotly(top20cases) ### Plotly is used with all graphs in able to display variable data when hovering over axes values

```


### Top 20 Recoveries

```{r}

#Arrange from high to low  

toprecoveries <- World_map_data %>% arrange(desc(Recoveries))

toprecoveries$Country.Region <- factor(toprecoveries$Country.Region , levels =toprecoveries$Country.Region[order(toprecoveries$Recoveries)])

# select and plot the first 20

top20rec <- toprecoveries[1:20,] %>% ggplot(aes(x=Country.Region, y=Recoveries)) +
  geom_bar(stat="identity", color="green",fill="green") + ggtitle("Global Top 20  Recoveries") + labs(y= "Total Confirmed Recoveries", x = "Country") + theme_bw() + theme(axis.text.x = element_text(angle = 45))
ggplotly(top20rec)

```


### Top 20 Deaths 

```{r}

# Sort from high to low and select top 20 
topdeaths <-  World_map_data %>% arrange(desc(Deaths))
topdeaths<- topdeaths[1:20,]

topdeaths$Country.Region <- factor(topdeaths$Country.Region , levels = topdeaths$Country.Region[order(topdeaths$Deaths)])

top20deaths <- topdeaths %>% ggplot(aes(x=Country.Region, y=Deaths)) +
  geom_bar(stat="identity", color="red",fill="red") + ggtitle("Global Top 20 Deaths") + labs(y= "Total Confirmed Cases", x = "Country") + theme_bw() + theme(axis.text.x = element_text(angle = 45))
ggplotly(top20deaths)

```




#South Africa
```{r include=FALSE}
RSA_covid <- read_csv("Merged Data/RSA_Covid.csv")
RSA_Pop<- read_csv("Merged Data/RSA_PopH.csv")

```

```{r include=FALSE}
RSA_Gender<- read_csv(file = "Data/Deaths_gender_RSA.csv")
RSA_Age<- read_csv(file = "Data/Deaths_Age_RSA.csv")
RSA_Age <- RSA_Age %>% slice(-n())
RSA_Tests<- read_csv(file="Merged Data/Test_RSA.csv")
```



```{r include=FALSE}
head(RSA_covid)

test2 <- RSA_covid %>% group_by(Province)%>% select(`Province`,`Cases`, `Recoveries`, `Deaths`) %>% slice(which.max(Cases)) %>% arrange(Cases,Recoveries)

```

```{r include=FALSE}
test3 <- test2 %>% 
  pivot_longer(c(`Cases`, `Recoveries`, `Deaths`), names_to = "Case_Type", values_to = "Total_Cases")

```

```{r include=FALSE}

# Provincial summary 
prov_sum <- test3 %>% ggplot(aes(fill=Case_Type, y=Total_Cases, x=Province)) + 
    geom_bar(stat="identity", position=position_dodge()) + facet_wrap(~ Province, scales = "free", ncol = 5 ) + 
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.title = element_text(hjust = 0.5,size = 20, face = "bold")) + labs(x = NULL, y=NULL, fill = "",title = "Cases by Province") + scale_fill_manual(values=c("#ADD8E6", "#FF0000", "#90EE90"))
prov_sum1<- ggplotly(prov_sum)

```


```{r include=FALSE}

RSA_covid$date<-as.Date(as.character(RSA_covid$date),format="%d-%m-%Y")
RSA_covid <- arrange(RSA_covid , date)

RSA_covid$Active_Cases <- RSA_covid$Cases - RSA_covid$Deaths - RSA_covid$Recoveries

#get the latest (newest) date in dataset and use as final break when plotting dates on Y-axis
recentdate = sqldf("SELECT 
              max(date) as 'max__Date'
              FROM RSA_covid", method = "name__class") 
# convert date to character
maxdate <- as.character(recentdate$max)


# use function to extract the last day of each month in a dataframe 
LastDayInMonth <- function(dt)
{
  dt <- (as.character(dt))
  dt <- as.character(as.Date(dt) %m+% months(1))
  dt <- as.Date(ISOdate(as.numeric(substr(dt, 1, 4)),
                        as.numeric(substr(dt, 6, 7)),
                        1) - days(1))
  return(dt)
}

# create a list of end-of-month dates to insert as breaks when plotting dates on Y-axis. See example on timeline charts
last_dates <- LastDayInMonth(RSA_covid$date)
last_dates1 <- unique(last_dates) 
Len_Dates<- length(last_dates1)
list <- c(last_dates1[-Len_Dates],recentdate$max) 

```

Column {data-width=650}
-----------------------------------------------------------------------

### Map Of Western Cape 

```{r}
#Printing map of Western Cape 
MapWC
```

Column {data-width=350}
--------

### Number of tests done 

```{r}
## Transforming the date column from character to a date 
RSA_Tests$date<- as.Date(as.character(RSA_Tests$date),format="%d-%m-%Y")

#Extracting the Max amount of Cumulative Tests. AKA the total tests 
RSA_Max_Test<- RSA_Tests %>% slice(which.max(cumulative_tests))

```

```{r}
#Putting total tests in a colour box as part of infographic 
valueBox(RSA_Max_Test$cumulative_tests, icon = "ion-erlenmeyer-flask", color = "gray")
```



### Positive Cases
```{r}
## Extracts the max values from the RSA COVID 19 data #Due to it being cumulative data Max should always be latest data
RSA_VB_Cases<- RSA_covid %>%
  group_by(date) %>%
  summarize(Cases = sum(Cases), Recoveries = sum(Recoveries),Deaths = sum(Deaths),Active_Cases = sum(Active_Cases)) %>% slice(which.max(Cases)) %>% select(Cases,Deaths,Recoveries)  

```

```{r}
#Putting Total cases into infographic 

valueBox(RSA_VB_Cases$Cases, icon = "ion-thermometer")

```



### Recoverd 

```{r}
#Putting Total cases into infographic 

valueBox(RSA_VB_Cases$Recoveries, icon = "ion-medkit", color = "green")

```



Column {data-width=350}
-----------------------------------------------------------------------

### South Africa Timeline 



```{r include=FALSE}
# Extracting the data from RSA COVID data and making a Time series for a plot
# First Group by dates
# Second get the totals for each day
# Plot the totals by day 

plotsa <- RSA_covid %>%
  group_by(date) %>%
  summarize(Cases = sum(Cases), Recoveries = sum(Recoveries),Deaths = sum(Deaths),Active_Cases = sum(Active_Cases)) %>% 
  na.omit()  %>% ggplot(aes(x = date)) + geom_line(aes(y=Cases,color = "Confirmed Cases"),size=1) + geom_line(aes(y= Active_Cases,color = "Active Cases"),size=1) + geom_line(aes(y=Recoveries,color = "Recoveries"), size=1) + geom_line(aes(y=Deaths,color = "Deaths"), size=1)+ scale_x_date(breaks = as.Date(list)) + scale_colour_manual(name = "",values = c("Confirmed Cases" = "#0000FF", "Active Cases" = "#add8e6", "Recoveries" = "#00FF00", "Deaths" = "#FF0000" )) + theme_bw() + theme(axis.text.x = element_text(angle = 45)) + labs(title="South Africa Timeline", x ="", y = "Confirmed Cases")

Line_RSA<-ggplotly(plotsa)

```

```{r}
Line_RSA
```




Column {data-width=350}
-----------------------------------------------------------------------
### Male Deaths 

```{r}
## Info Graphic of Male Deaths

valueBox(RSA_Gender$male, icon = "ion-male")
```


### Female Deaths 

```{r}

valueBox(RSA_Gender$female, icon = "ion-female", color = "pink")
```

### Deaths 

```{r}
#Putting Total Deaths into infographic 

#ion-sad-outline

valueBox(RSA_VB_Cases$Deaths, icon = "ion-heart-broken", color = "red")
```



Column {data-width=350}
-----------------------------------------------------------------------

### South Africa Deaths By Age

```{r}

### Creating Bar Chart of Deaths By Age For RSA

plotage <- RSA_Age %>% ggplot(aes(x=Age, y=Deaths)) +
  geom_bar(stat="identity", color="red") + ggtitle("South Africa Total Deaths per age group") +theme_bw()

PlotAGE<- ggplotly(plotage)

```


```{r}
PlotAGE
```

### Tests VS Positive Cases 

```{r}

time <- read_csv("Merged Data/RSA_Covid.csv")

time$date<-as.Date(as.character(time$date),format="%d-%m-%Y")
time$Active_Cases <- time$Cases - time$Deaths - time$Recoveries

sa <- time %>%
  group_by(date) %>%
  summarize(Cases = sum(Cases), Recoveries = sum(Recoveries),Deaths = sum(Deaths),Active_Cases = sum(Active_Cases)) 

#merge 2 data sets
b <- read_csv("Data/Test_RSA.csv")
b$date<-as.Date(as.character(b$date),format="%d-%m-%Y")
merged <- sa %>% left_join(b, by = "date") 


#get aggregate weeks
sa2 <- merged %>% group_by(week = cut(date , "week")) %>% summarise(Cases = mean(Cases),min_date = min(date), max_date = max(date), tests = mean(cumulative_tests))


# calculate increase in cases per week
sa3 = sa2 %>%
  arrange(week) %>%
  mutate(
         Positive_Cases = ceiling( Cases - lag(Cases)), Total_Tests = ceiling(tests - lag(tests)))


# create x axis week date
begin_date <- paste(as.character(day(sa3$min_date)) , as.character(month(sa3$min_date)),sep='/')
end_date <- paste(as.character(day(sa3$max_date)) , as.character(month(sa3$max_date)),sep='/')
sa3$week_date <- paste(begin_date,end_date,sep=" - ")

sa3$week_date <- factor(sa3$week_date, levels = sa3$week_date[order(sa3$Cases)])

sa4 <- sa3 %>% na.omit() 

#plot both total tests and cases on the Y-axes
plotsa4 <- sa4 %>% ggplot(aes(x=week_date)) +
  geom_bar(aes(y=Total_Tests,colour="Total Tests"),stat="identity" , fill = "blue") + geom_bar(aes(y=Positive_Cases,colour = "Positive Cases"),stat="identity", fill = "red") + ggtitle("SA weekly total tests VS new confirmed positive cases") + labs(y= "Total New Confirmed Cases", x = "Week") + scale_colour_manual(values = c("Total Tests" = "blue", "Positive Cases"= "red")) + labs(y = "No of Cases",x = "Week",colour = "Legend") + theme_bw() + theme(axis.text.x = element_text(angle = 45)) 
ggplotly(plotsa4)
```


# Provincial 


```{r include= FALSE}
RSA_Pop$Pop_Dev<- RSA_Pop$Population/100000

```
Column {data-width=350}
-----------------------------------------------------------------------

### Provincial Summary 

```{r}
# written at start of the script 

prov_sum1
```


```{r include=F}
infect_Prov<-RSA_covid %>% group_by(Province) %>% slice(which.max(Cases)) %>% select(Province,Cases,Deaths,Recoveries) %>% arrange(Cases) 

infect_Prov$Province<- factor(infect_Prov$Province, levels = infect_Prov$Province[order(infect_Prov$Cases)])

```


Column {data-width=350}
-----------------------------------------------------------------------
### Bar Chart of Infections By Province 


```{r}
infect_Prov$Province <- factor(infect_Prov$Province, levels = infect_Prov$Province[order(infect_Prov$Cases)])

bar_Cases <- infect_Prov %>% ggplot(aes(x=Province, y=Cases)) +
  geom_bar(stat="identity", color="blue",fill="blue") + ggtitle("Provincial Total Confirmed Cases") + labs(y= "Total Cases", x = "Province") + theme_bw() + coord_flip() 
bar_CasesP<- ggplotly(bar_Cases)

```
```{r}
bar_CasesP
```

### Bar Chart of Recoveries By Province 

```{r}
infect_Prov$Province <- factor(infect_Prov$Province, levels = infect_Prov$Province[order(infect_Prov$Recoveries)])

bar_Rec <- infect_Prov %>% na.omit() %>% ggplot(aes(x=Province, y=Recoveries)) +
  geom_bar(stat="identity", color="green",fill="green") + ggtitle("Provincial Total Confirmed Recoveries") + labs(y= "Total Recoveries", x = "Province") + theme_bw() + coord_flip()
bar_RecP<- ggplotly(bar_Rec)
```
```{r}
bar_RecP
```

### Bar Chart of Deaths By Province 

```{r}
infect_Prov$Province <- factor(infect_Prov$Province, levels = infect_Prov$Province[order(infect_Prov$Deaths)])
bar_Death <- infect_Prov %>% ggplot(aes(x=Province, y=Deaths)) +
  geom_bar(stat="identity", color="red",fill="red") + ggtitle("Provincial Total Confirmed Deaths") + labs(y= "Total Deaths", x = "Province") + theme_bw() + coord_flip()
bar_deatP<-ggplotly(bar_Death)
```

```{r}
bar_deatP
```


Row 
--------
### Section
```{r}
valueBox("Eastern Cape ", color = "orange")
```


Row 
--------

### Eastern Cape Infections Per 100 000 People

```{r}
gauge(round(as.numeric(infect_Prov[infect_Prov$Province=="EC",2])/as.numeric(RSA_Pop[RSA_Pop$Province=="Eastern Cape",4]),digits = 0),min = 0 , max= 100000)
```

### Eastern Cape Proportion of RSA's total Cases 



```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="EC",2]),min = 0 , max=RSA_VB_Cases$Cases, gaugeSectors(success = c(0,RSA_VB_Cases$Cases*0.10),warning = c(RSA_VB_Cases$Cases*0.101,RSA_VB_Cases$Cases*0.3),danger = c(RSA_VB_Cases$Cases*0.301,RSA_VB_Cases$Cases)))
```

### Eastern Cape Proportion of RSA's total Deaths

```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="EC",3]),min = 0 , max=RSA_VB_Cases$Deaths, gaugeSectors(success = c(0,RSA_VB_Cases$Deaths*0.10),warning = c(RSA_VB_Cases$Deaths*0.101,RSA_VB_Cases$Deaths*0.3),danger = c(RSA_VB_Cases$Deaths*0.301,RSA_VB_Cases$Deaths)))
```



Column {data-width=350}
--------
###EC
```{r include=FALSE}
plotec <- RSA_covid %>% subset(Province == "EC") %>%  na.omit()  %>% ggplot(aes(x = date)) + geom_line(aes(y=Cases,color = "Confirmed Cases"),size=1) + geom_line(aes(y= Active_Cases,color = "Active Cases"),size=1) + geom_line(aes(y=Recoveries,color = "Recoveries"), size=1) + geom_line(aes(y=Deaths,color = "Deaths"), size=1)+ scale_x_date(breaks = as.Date(list)) + scale_colour_manual(name = "",values = c("Confirmed Cases" = "#0000FF", "Active Cases" = "#add8e6", "Recoveries" = "#00FF00", "Deaths" = "#FF0000" )) + theme_bw() + theme(axis.text.x = element_text(angle = 45)) + labs(title="Eastern Cape Timeline", x ="", y = "")

Line_EC<- ggplotly(plotec)
```
```{r}
Line_EC
```



Row 
--------
### Section
```{r}
valueBox("Western Cape ", color = "orange")
```

Row 
--------

### Western Cape Infections Per 100 000 People

```{r}
gauge(round(as.numeric(infect_Prov[infect_Prov$Province=="WC",2])/as.numeric(RSA_Pop[RSA_Pop$Province=="Western Cape",4]),digits = 0),min = 0 , max= 100000)
```

### Western Cape Proportion of RSA's total Cases 


```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="WC",2]),min = 0 , max=RSA_VB_Cases$Cases,
      gaugeSectors(success = c(0,RSA_VB_Cases$Cases*0.10),warning = c(RSA_VB_Cases$Cases*0.101,RSA_VB_Cases$Cases*0.3),danger = c(RSA_VB_Cases$Cases*0.301,RSA_VB_Cases$Cases)))
```

### Western Cape Proportion of RSA's total Deaths

```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="WC",3]),min = 0 , max=RSA_VB_Cases$Deaths,
      gaugeSectors(success = c(0,RSA_VB_Cases$Deaths*0.10),warning = c(RSA_VB_Cases$Deaths*0.101,RSA_VB_Cases$Deaths*0.3),danger = c(RSA_VB_Cases$Deaths*0.301,RSA_VB_Cases$Deaths)))
```

Column {data-width=350}
--------

### WC
```{r include=FALSE}
plotwc <- RSA_covid %>% subset(Province == "WC") %>%  na.omit()  %>% ggplot(aes(x = date)) + geom_line(aes(y=Cases,color = "Confirmed Cases"),size=1) + geom_line(aes(y= Active_Cases,color = "Active Cases"),size=1) + geom_line(aes(y=Recoveries,color = "Recoveries"), size=1) + geom_line(aes(y=Deaths,color = "Deaths"), size=1)+ scale_x_date(breaks = as.Date(list)) + scale_colour_manual(name = "",values = c("Confirmed Cases" = "#0000FF", "Active Cases" = "#add8e6", "Recoveries" = "#00FF00", "Deaths" = "#FF0000" )) + theme_bw() + theme(axis.text.x = element_text(angle = 45)) + labs(title="Western Cape Timeline", x ="", y = "")

Line_WC<-ggplotly(plotwc)

```
```{r}
Line_WC
```

Row 
--------

### Section
```{r}
valueBox("Free State  ", color = "orange")
```

Row
-----


### Free State Infections Per 100 000 People

```{r}
gauge(round(as.numeric(infect_Prov[infect_Prov$Province=="FS",2])/as.numeric(RSA_Pop[RSA_Pop$Province=="Free State",4]),digits = 0),min = 0 , max= 100000)
```


### Free State Proportion of RSA's total Cases 



```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="FS",2]),min = 0 , max=RSA_VB_Cases$Cases,
      gaugeSectors(success = c(0,RSA_VB_Cases$Cases*0.10),warning = c(RSA_VB_Cases$Cases*0.101,RSA_VB_Cases$Cases*0.3),danger = c(RSA_VB_Cases$Cases*0.301,RSA_VB_Cases$Cases)))
```

### Free State Proportion of RSA's total Deaths

```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="FS",3]),min = 0 , max=RSA_VB_Cases$Deaths,
      gaugeSectors(success = c(0,RSA_VB_Cases$Deaths*0.10),warning = c(RSA_VB_Cases$Deaths*0.101,RSA_VB_Cases$Deaths*0.3),danger = c(RSA_VB_Cases$Deaths*0.301,RSA_VB_Cases$Deaths)))
      
```


Column {data-width=350}
--------
### Free State 

```{r include=FALSE}
plotfs <- RSA_covid %>% subset(Province == "FS") %>%  na.omit()  %>% ggplot(aes(x = date)) + geom_line(aes(y=Cases,color = "Confirmed Cases"),size=1) + geom_line(aes(y= Active_Cases,color = "Active Cases"),size=1) + geom_line(aes(y=Recoveries,color = "Recoveries"), size=1) + geom_line(aes(y=Deaths,color = "Deaths"), size=1)+ scale_x_date(breaks = as.Date(list)) + scale_colour_manual(name = "",values = c("Confirmed Cases" = "#0000FF", "Active Cases" = "#add8e6", "Recoveries" = "#00FF00", "Deaths" = "#FF0000" )) + theme_bw() + theme(axis.text.x = element_text(angle = 45)) + labs(title="Free State Timeline", x ="", y = "")

Line_FS<-ggplotly(plotfs)

```
```{r}
Line_FS
```


Row 
--------
### Section
```{r}
valueBox("Gauteng  ", color = "orange")
```

Row
-----


### Gauteng Infections Per 100 000 People

```{r}
gauge(round(as.numeric(infect_Prov[infect_Prov$Province=="GP",2])/as.numeric(RSA_Pop[RSA_Pop$Province=="Gauteng",4]),digits = 0),min = 0 , max= 100000)
```

### Gauteng Proportion of RSA's total Cases 



```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="GP",2]),min = 0 , max=RSA_VB_Cases$Cases,
      gaugeSectors(success = c(0,RSA_VB_Cases$Cases*0.10),warning = c(RSA_VB_Cases$Cases*0.101,RSA_VB_Cases$Cases*0.3),danger = c(RSA_VB_Cases$Cases*0.301,RSA_VB_Cases$Cases)))
```

### Gauteng Proportion of RSA's total Deaths

```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="GP",3]),min = 0 , max=RSA_VB_Cases$Deaths,
      gaugeSectors(success = c(0,RSA_VB_Cases$Deaths*0.10),warning = c(RSA_VB_Cases$Deaths*0.101,RSA_VB_Cases$Deaths*0.3),danger = c(RSA_VB_Cases$Deaths*0.301,RSA_VB_Cases$Deaths)))
      
```




Column {data-width=350}
------

### GP

```{r include=FALSE}
plotgp <- RSA_covid %>% subset(Province == "GP") %>%  na.omit()  %>% ggplot(aes(x = date)) + geom_line(aes(y=Cases,color = "Confirmed Cases"),size=1) + geom_line(aes(y= Active_Cases,color = "Active Cases"),size=1) + geom_line(aes(y=Recoveries,color = "Recoveries"), size=1) + geom_line(aes(y=Deaths,color = "Deaths"), size=1)+ scale_x_date(breaks = as.Date(list)) + scale_colour_manual(name = "",values = c("Confirmed Cases" = "#0000FF", "Active Cases" = "#add8e6", "Recoveries" = "#00FF00", "Deaths" = "#FF0000" )) + theme_bw() + theme(axis.text.x = element_text(angle = 45)) + labs(title="Gauteng Timeline", x ="", y = "")

Line_GP<-ggplotly(plotgp)

```
```{r}
Line_GP
```

Row
------

### Section
```{r}
valueBox("KwaZulu Natal  ", color = "orange")
```

Row
------

### KwaZulu-Natal Infections Per 100 000 People

```{r}
gauge(round(as.numeric(infect_Prov[infect_Prov$Province=="KZN",2])/as.numeric(RSA_Pop[RSA_Pop$Province=="KwaZulu-Natal",4]),digits = 0),min = 0 , max= 100000)
```


### KwaZulu Natal Proportion of RSA's total Cases 


```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="KZN",2]),min = 0 , max=RSA_VB_Cases$Cases,
      gaugeSectors(success = c(0,RSA_VB_Cases$Cases*0.10),warning = c(RSA_VB_Cases$Cases*0.101,RSA_VB_Cases$Cases*0.3),danger = c(RSA_VB_Cases$Cases*0.301,RSA_VB_Cases$Cases)))
```

### KwaZulu Natal Proportion of RSA's total Deaths

```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="KZN",3]),min = 0 , max=RSA_VB_Cases$Deaths,
      gaugeSectors(success = c(0,RSA_VB_Cases$Deaths*0.10),warning = c(RSA_VB_Cases$Deaths*0.101,RSA_VB_Cases$Deaths*0.3),danger = c(RSA_VB_Cases$Deaths*0.301,RSA_VB_Cases$Deaths)))
      
```


Column {data-width=350}
------

###KZN
```{r include=FALSE}
plotkzn <- RSA_covid %>% subset(Province == "KZN") %>%  na.omit()  %>% ggplot(aes(x = date)) + geom_line(aes(y=Cases,color = "Confirmed Cases"),size=1) + geom_line(aes(y= Active_Cases,color = "Active Cases"),size=1) + geom_line(aes(y=Recoveries,color = "Recoveries"), size=1) + geom_line(aes(y=Deaths,color = "Deaths"), size=1)+ scale_x_date(breaks = as.Date(list)) + scale_colour_manual(name = "",values = c("Confirmed Cases" = "#0000FF", "Active Cases" = "#add8e6", "Recoveries" = "#00FF00", "Deaths" = "#FF0000" )) + theme_bw() + theme(axis.text.x = element_text(angle = 45)) + labs(title="KwaZulu Natal   Timeline", x ="", y = "")

Line_KZN<-ggplotly(plotkzn)

```
```{r}
Line_KZN
```


Row
-------
### Section

```{r}
valueBox("Limpopo  ", color = "orange")
```

Row
-----

### Limpopo Infections Per 100 000 People

```{r}
gauge(round(as.numeric(infect_Prov[infect_Prov$Province=="LP",2])/as.numeric(RSA_Pop[RSA_Pop$Province=="Limpopo",4]),digits = 0),min = 0 , max= 100000)
```


### Limpopo Proportion of RSA's total Cases 


```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="LP",2]),min = 0 , max=RSA_VB_Cases$Cases,
      gaugeSectors(success = c(0,RSA_VB_Cases$Cases*0.10),warning = c(RSA_VB_Cases$Cases*0.101,RSA_VB_Cases$Cases*0.3),danger = c(RSA_VB_Cases$Cases*0.301,RSA_VB_Cases$Cases)))
```

### Limpopo Proportion of RSA's total Deaths

```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="LP",3]),min = 0 , max=RSA_VB_Cases$Deaths,
      gaugeSectors(success = c(0,RSA_VB_Cases$Deaths*0.10),warning = c(RSA_VB_Cases$Deaths*0.101,RSA_VB_Cases$Deaths*0.3),danger = c(RSA_VB_Cases$Deaths*0.301,RSA_VB_Cases$Deaths)))
      
```





Column {data-width=350}
------

### Limpopo
```{r include=FALSE}
plotlp <- RSA_covid %>% subset(Province == "LP") %>%  na.omit()  %>% ggplot(aes(x = date)) + geom_line(aes(y=Cases,color = "Confirmed Cases"),size=1) + geom_line(aes(y= Active_Cases,color = "Active Cases"),size=1) + geom_line(aes(y=Recoveries,color = "Recoveries"), size=1) + geom_line(aes(y=Deaths,color = "Deaths"), size=1)+ scale_x_date(breaks = as.Date(list)) + scale_colour_manual(name = "",values = c("Confirmed Cases" = "#0000FF", "Active Cases" = "#add8e6", "Recoveries" = "#00FF00", "Deaths" = "#FF0000" )) + theme_bw() + theme(axis.text.x = element_text(angle = 45)) + labs(title="Limpopo  Timeline", x ="", y = "")

Line_LP<-ggplotly(plotlp)

```
```{r}
Line_LP
```

Row
-------
### Section

```{r}
valueBox("Mpumalanga  ", color = "orange")
```

Row
-----

### Mpumalanga Infections Per 100 000 People

```{r}
gauge(round(as.numeric(infect_Prov[infect_Prov$Province=="MP",2])/as.numeric(RSA_Pop[RSA_Pop$Province=="Mpumalanga",4]),digits = 0),min = 0 , max= 100000)
```

### Mpumalanga Proportion of RSA's total Cases 


```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="MP",2]),min = 0 , max=RSA_VB_Cases$Cases,
      gaugeSectors(success = c(0,RSA_VB_Cases$Cases*0.10),warning = c(RSA_VB_Cases$Cases*0.101,RSA_VB_Cases$Cases*0.3),danger = c(RSA_VB_Cases$Cases*0.301,RSA_VB_Cases$Cases)))
```

### Mpumalanga Proportion of RSA's total Deaths

```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="MP",3]),min = 0 , max=RSA_VB_Cases$Deaths,
      gaugeSectors(success = c(0,RSA_VB_Cases$Deaths*0.10),warning = c(RSA_VB_Cases$Deaths*0.101,RSA_VB_Cases$Deaths*0.3),danger = c(RSA_VB_Cases$Deaths*0.301,RSA_VB_Cases$Deaths)))
      
```




Column {data-width=350}
------
### Mpumalanga
```{r include=FALSE}
plotmp <- RSA_covid %>% subset(Province == "MP") %>%  na.omit()  %>% ggplot(aes(x = date)) + geom_line(aes(y=Cases,color = "Confirmed Cases"),size=1) + geom_line(aes(y= Active_Cases,color = "Active Cases"),size=1) + geom_line(aes(y=Recoveries,color = "Recoveries"), size=1) + geom_line(aes(y=Deaths,color = "Deaths"), size=1)+ scale_x_date(breaks = as.Date(list)) + scale_colour_manual(name = "",values = c("Confirmed Cases" = "#0000FF", "Active Cases" = "#add8e6", "Recoveries" = "#00FF00", "Deaths" = "#FF0000" )) + theme_bw() + theme(axis.text.x = element_text(angle = 45)) + labs(title="Mpumalanga Timeline", x ="", y = "")

Line_MP<-ggplotly(plotmp)

```
```{r}
Line_MP
```


Row
-------
### Section

```{r}
valueBox("Northern Cape  ", color = "orange")
```

Row
-----

### Northern Cape Infections Per 100 000 People

```{r}
gauge(round(as.numeric(infect_Prov[infect_Prov$Province=="NC",2])/as.numeric(RSA_Pop[RSA_Pop$Province=="Northern Cape",4]),digits = 0),min = 0 , max= 100000)
```

### Northern Cape  Proportion of RSA's total Cases 


```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="NC",2]),min = 0 , max=RSA_VB_Cases$Cases,
      gaugeSectors(success = c(0,RSA_VB_Cases$Cases*0.10),warning = c(RSA_VB_Cases$Cases*0.101,RSA_VB_Cases$Cases*0.3),danger = c(RSA_VB_Cases$Cases*0.301,RSA_VB_Cases$Cases)))
```

### Northern Cape  Proportion of RSA's total Deaths

```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="NC",3]),min = 0 , max=RSA_VB_Cases$Deaths,
      gaugeSectors(success = c(0,RSA_VB_Cases$Deaths*0.10),warning = c(RSA_VB_Cases$Deaths*0.101,RSA_VB_Cases$Deaths*0.3),danger = c(RSA_VB_Cases$Deaths*0.301,RSA_VB_Cases$Deaths)))
      
```


Column {data-width=350}
------
### Northern Cape 

```{r include=FALSE}
plotnc <- RSA_covid %>% subset(Province == "NC") %>%  na.omit()  %>% ggplot(aes(x = date)) + geom_line(aes(y=Cases,color = "Confirmed Cases"),size=1) + geom_line(aes(y= Active_Cases,color = "Active Cases"),size=1) + geom_line(aes(y=Recoveries,color = "Recoveries"), size=1) + geom_line(aes(y=Deaths,color = "Deaths"), size=1)+ scale_x_date(breaks = as.Date(list)) + scale_colour_manual(name = "",values = c("Confirmed Cases" = "#0000FF", "Active Cases" = "#add8e6", "Recoveries" = "#00FF00", "Deaths" = "#FF0000" )) + theme_bw() + theme(axis.text.x = element_text(angle = 45)) + labs(title="Northern Cape Timeline", x ="", y = "")

Line_NC<-ggplotly(plotnc)

```
```{r}
Line_NC
```



Row
-------
### Section

```{r}
valueBox("Northwest  ", color = "orange")
```

Row
-----
### Northwest Infections Per 100 000 People

```{r}
gauge(round(as.numeric(infect_Prov[infect_Prov$Province=="NW",2])/as.numeric(RSA_Pop[RSA_Pop$Province=="Northwest",4]),digits = 0),min = 0 , max= 100000)
```


### Northwest  Proportion of RSA's total Cases 


```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="NW",2]),min = 0 , max=RSA_VB_Cases$Cases,
      gaugeSectors(success = c(0,RSA_VB_Cases$Cases*0.10),warning = c(RSA_VB_Cases$Cases*0.101,RSA_VB_Cases$Cases*0.3),danger = c(RSA_VB_Cases$Cases*0.301,RSA_VB_Cases$Cases)))
```

### North West  Proportion of RSA's total Deaths

```{r}
gauge(as.numeric(infect_Prov[infect_Prov$Province=="NW",3]),min = 0 , max=RSA_VB_Cases$Deaths,
      gaugeSectors(success = c(0,RSA_VB_Cases$Deaths*0.10),warning = c(RSA_VB_Cases$Deaths*0.101,RSA_VB_Cases$Deaths*0.3),danger = c(RSA_VB_Cases$Deaths*0.301,RSA_VB_Cases$Deaths)))
      
```


Column {data-width=350}
------

###North West
```{r include=FALSE}
plotnw <- RSA_covid %>% subset(Province == "NW") %>%  na.omit()  %>% ggplot(aes(x = date)) + geom_line(aes(y=Cases,color = "Confirmed Cases"),size=1) + geom_line(aes(y= Active_Cases,color = "Active Cases"),size=1) + geom_line(aes(y=Recoveries,color = "Recoveries"), size=1) + geom_line(aes(y=Deaths,color = "Deaths"), size=1)+ scale_x_date(breaks = as.Date(list)) + scale_colour_manual(name = "",values = c("Confirmed Cases" = "#0000FF", "Active Cases" = "#add8e6", "Recoveries" = "#00FF00", "Deaths" = "#FF0000" )) + theme_bw() + theme(axis.text.x = element_text(angle = 45)) + labs(title="North West Timeline", x ="", y = "")

Line_NW<-ggplotly(plotnw)

```
```{r}
Line_NW
```





